Maybe Slipstreams

### 2014-03-14 paper.tex
article type again with no date, looks better

\documentclass[twocolumn]{paper}
\usepackage{authblk}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{cite}
\usepackage[margin=1.0in]{geometry}
\lstset{language=Haskell}

\title{Maybe Slipstreams}
\author[*]{Morgan McDermott}
\author[*]{John Carlyle}
\affil[*]{University of flightless dragons}

@@

\section{Introduction}
\subsection{What is FRP}
Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on the key concepts of time varying values.   These values can also be considered events depending on the granularity of the stream. Reactivity is defined as a reaction to an event; when a node recieves a new value it reacts by changing its value. FRP is particularly well suited for transforming data and data structures since it is, by nature, a collection of pure functions.

>>>>

\documentclass[twocolumn,11pt,english]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{cite}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\lstset{language=Haskell}

\title{Maybe Slipstreams}
\date{}
\author{
  Carlyle, John\\
  \textit{jcarlyle@ucsc.edu}
  \and
  McDermott, Morgan\\
  \textit{mmcdermo@ucsc.edu}
}

@@

\section{Introduction}
\subsection{What is FRP}
Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on time varying values.
